Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
Remark 1.6 is now Definition 1.6

\begin{remark}
\label{rem:dimTypeCone}
Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).
We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
\end{remark}

>>>>

Since the type cone is an~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets (thus~$N-n$ extremal adjacent pairs).

\begin{definition}
\label{rem:dimTypeCone}
The type cone is \defn{simplicial} if it has precisely $N-n$ facets.
\end{definition}
